\chapter*{Preface}
Many electronic applications have signal processing as an important part of the system. The theme of this semester is \ldots. The level is a 1\textsuperscript{st} semester M.Sc project rated to 15 ECTS-points within AD:MT at Aalborg University.
The target group of this report are supervisors and future developers of audio technologies such as students and other interested parties within the School of Information and Communication Technology at the The Faculty of Engineering and Science.
The central aspects of this project are dealing with design considerations \ldots bla bla.
\section*{Reading Guide}
The report is a worksheet for an article and therefore the structure is loose. There is one part called Worksheet.
%
% List of the four parts
% 
    % \begin{itemize}
    % \item I Analysis 
    % \item II Design and Implementation
    % % \item III Implementation
    % % \item IV Appendices
    % \end{itemize}

The Analysis will be dealing with definition of the technology which will be developed and therefore it contains the necessary discussions for a Requirement Specification, which will result in guidelines and instructions for the Design and Implementation part. The Design and Implementation part contains development of the system which is implemented in the DSP and solutions to the issues discussed. %The Discussion part contains a summary and conclusion, and reflections regarding the obtained system technology.

\subsection*{Appendices}
Appendices are found after the main report \fixme{insert reference} and on the attached CD. The appendices contains all source code, an extended analysis, measurement reports and work sheets. The CD also contains a digital version of the report and the web pages used. A complete list of the CD content can be found here \fixme{insert ref}. When referred to the CD the following symbol is used \cdref{path/to/stuff} 

All figures, tables and equations are referred to by the number of the chapter they are used in, followed by a number indicating the number of figure, table or equation in the specific chapter. Hence each figure has a unique number, which is also printed at the bottom of the figure along with a caption. The same applies to tables and equations, the latter of which have no captions. Appendices are referred to by capital letters instead of chapter numbers.

\subsection*{Bibliography} At the very end of the main report, a Bibliography is listed which contains all sources of information used in the report. In the Bibliography books are indicated with author, title, publisher and year. Web pages are indicated with author and title. All information sources are referred to by the number which they feature in the list. This will look like this: [number]. If the sources reference is written just before a final dot, then it represents the source of information for the sentence in question. If the reference is placed after the dot it represents the source of information for the section in question. 

